О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-27 pps-linear-bound/pps-linear-lower-bound.tex
Proofreading by Usachev - p. 5

\begin{lemma}
	\label{lem:2k-1_segments}
	Let $M \in \mathfrak{M}(2,\mathbb{N})$ and let $m$ be a straight line.
	Then for every $k\in\mathbb{N}$ there are at most $2k-1$ segments $\Delta_i \subset m$ with endpoints in $M$,
	such that $|\Delta_i| = k$.
\end{lemma}
\begin{proof}
	Consider a point $N\in M \setminus m$.
	Then for each $\Delta_i$ there is a $\rho(n_i,\Delta_i)$-curve containing $N$.
	Due to Proposition~\ref{obs:rho_curves}, all $n_i$ are distinct;
	otherwise $\rho(n_i,\Delta_i)$-curve and $\rho(n_i,\Delta_j)$-curve, $j\neq i$, do not intersect.
	There can be only $2k-1$ distinct values for $n_i$,
	so there are at most $2k-1$ distinct segments $\Delta_i$.
\end{proof}

@@

\begin{proof}
	Any $n^2+1$ points, including the endpoints of $\Delta$, split the segment $\Delta$ into $n^2$
	sequential segments $\Delta_i$.
	Due to Lemma~\ref{lem:2k-1_segments}, there is at most one segment of length 1,
	at most three segments of length 2, etc.
	The following two values of sums conclude the proof:
	\begin{equation}
		1 + \sum_{k=1}^n (2k-1) = n^2 + 1
		,
	\end{equation}
	\begin{equation}
		\sum_{k=1}^n k(2k-1) = \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n
		.
	\end{equation}
\end{proof}

Now we will estimate the length of a line segment that shares an arbitrary number of points
with an integral point set.

@@

\begin{proof}
	Let $f(k)$ denote the mininal length of a line segment
	that shares $k$ points with an integral point set.
	We observe that $f(k) > f (k-1)$.
	Due to Lemma~\ref{lem:line_segment_with n_squared_plus_one_points},
	$f(n^2+1) \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n$.

>>>>

\begin{lemma}
	\label{lem:2k-1_segments}
	Let $M \in \mathfrak{M}(2,\mathbb{N})$ and let $m$ be a straight line.
	Then for every $k\in\mathbb{N}$ there are at most $2k-1$ segments $\Delta_i \subset m$ with endpoints in $M$,
	such that $|\Delta_i| = k$.
\end{lemma}
\begin{proof}
	Consider a point $N\in M \setminus m$.
	Then for each $\Delta_i$ there is a $\rho(n_i,\Delta_i)$-curve containing $N$.
	Due to Proposition~\ref{obs:rho_curves}, all $n_i$ are distinct;
	otherwise the $\rho(n_i,\Delta_i)$-curve and the $\rho(n_i,\Delta_j)$-curve, $j\neq i$, do not intersect.
	There can be only $2k-1$ distinct values for $n_i$,
	so there are at most $2k-1$ distinct segments $\Delta_i$.
\end{proof}

@@

\begin{proof}
	Any $n^2+1$ points, including the endpoints of $\Delta$, partition the segment $\Delta$ into $n^2$
	sequential segments $\Delta_i$.
	Due to Lemma~\ref{lem:2k-1_segments}, there is at most one segment of length 1,
	at most three segments of length 2, etc.
	The following two expressions for sums conclude the proof:
	\begin{equation}
		1 + \sum_{k=1}^n (2k-1) = n^2 + 1
		,
	\end{equation}
	\begin{equation}
		\sum_{k=1}^n k(2k-1) = \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n
		.
	\end{equation}
\end{proof}

Now we will estimate the length of a line segment that intersects an integral point set
by an arbitrary number of points.

@@

\begin{proof}
	Let $f(k)$ denote the mininal length of a line segment
	that intersects an integral point set by $k$ points.
	We observe that $f(k) > f (k-1)$.
	Due to Lemma~\ref{lem:line_segment_with n_squared_plus_one_points},
	$f(n^2+1) \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n$.
